---
title: "X.X million workers likely lost their employer-provided health insurance over the past 10 weeks"
author: "Josh Bivens and Ben Zipperer"
date: "5/28/2020"
output:
  html_document:
    theme: flatly
---

```{r setup, include=FALSE}
library(knitr)
library(DT)
library(tidyverse)
library(scales)
opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}
ephi_industry <- read_csv("ephi_industry.csv") %>% 
  transmute(
    Industry = sectorname,
    `Total job losses (UI initial claims)` = number(emp_change, accuracy = 1.0, big.mark = ","),
    `Share of workers with EPHI` = percent(ephi_rate, accuracy = 0.1),
    `EPHI job losses` = number(ephi_change, accuracy = 1.0, big.mark = ","),
    `Total job losses as a share of industry employment` = percent(emp_change_share, accuracy = 0.1)
  )

ephi_state <- read_csv("ephi_state.csv") %>% 
  transmute(
    `State` = statename, 
    `Total job losses (UI initial claims)` = number(emp_change, accuracy = 1.0, big.mark = ","), 
    `EPHI job losses` = number(ephi_change, accuracy = 1.0, big.mark = ","),
    `Total job losses as a share of industry employment` = percent(emp_change_share, accuracy = 0.1)
  ) %>% 
  arrange(State)

```

## Tables

### Table 1: New UI claims and employer-provided health insurance losses between March 15 and May 23, by industry
```{r us_claims}
datatable(
  ephi_industry,
  elementId = "ephi-losses-industry",
  rownames = FALSE, 
  extensions = 'Buttons',
  options = list(
    buttons = list(list(extend = 'csv', filename= 'table2')),
    dom = 'Brt',
    columnDefs = list(
      list(className = 'dt-left', width = '20%', targets = 0),
      list(className = 'dt-right', width = '20%', targets = 1:4)
    ),
    scrollY = "300px",
    scrollCollapse = TRUE,
    paging = FALSE
  )
) %>% 
  formatStyle(
  "Industry",
  target = 'row',
  backgroundColor = styleEqual("All industries", 'gray'))
```
Source: Authors' analysis of state-level [UI claims](https://economic.github.io/ui_state_detailed/), US Department of Labor [UI Claims](https://www.dol.gov/ui/data.pdf), Quarterly Census of Employment and Wages [data](https://www.bls.gov/cew/downloadable-data-files.htm), and the 2018 Annual Social and Economic Supplement to the [Current Population Survey](https://thedataweb.rm.census.gov/ftp/cps_ftp.html#cpsmarch).

### Table 2. Estimated new UI claims and employer-provided health insurance losses between March 15 and May 23, by state
```{r}
ephi_state %>% 
  datatable(
    elementId = "ephi-losses-state",
    rownames = FALSE, 
    extensions = 'Buttons',
    options = list(
      buttons = list(list(extend = 'csv', filename= 'table3')),
      dom = 'Brt',
      columnDefs = list(
        list(className = 'dt-left', width = '20%', targets = 0),
        list(className = 'dt-right', width = '20%', targets = 1:3)
      ),
      scrollY = "300px",
      scrollCollapse = TRUE,
      paging = FALSE
    )
  )
```
Source: Authors' analysis of state-level [UI claims](https://economic.github.io/ui_state_detailed/), US Department of Labor [UI Claims](https://www.dol.gov/ui/data.pdf), Quarterly Census of Employment and Wages [data](https://www.bls.gov/cew/downloadable-data-files.htm), and the 2018 Annual Social and Economic Supplement to the [Current Population Survey](https://thedataweb.rm.census.gov/ftp/cps_ftp.html#cpsmarch).
